Contracts for Contracts

### 2023-03-02 paper.tex
misc

Smart contracts are programs to automate the execution of agreement so that all
parties involved in the agreement can be certain about the outcome.
Smart contracts are ``smart'' since by using blockchains they provide a
mechanism to \emph{ensure the economic outcome of transactions} without a
central authority.
A blockchain implements a consensus protocol of Byzantine-fault-tolerant
distributed ledgers.

@@

For example, Solidity provides first-order assertion primitives @require@ and
@assert@, but they cannot check function values (e.g. used as callbacks), which are a
common pattern used in smart contract programs. Attackers are able to utilize
the callback mechanism to \note{do crazy things and steal money}
Solidity also provides the @modifier@ mechanism that intercepts
before and after a function call, thus can be used to check
pre- and post-conditions.
\todo{can we compose modifier?}
\todo{can we attach modifier to callbacks?}
\todo{can we use modifier to check function's argument?}

The lack of sufficient linguistic means to specify and enforce subtle behaviors
discourages programmers to use higher-level abstractions when writing smart
contract code.
Instead, to be secure, programmers are obliged to write verbose code with
lower-level abstractions, which conflates the main business logic and
behavioral checks, leading to poor readability and maintainability.
For instance, to defend the famous DAO attack \note{cite} caused by allowing ``reentrancy''
via external functions, programmers have to be extra cautious about the execution
order or maintain additional states to check if a call is allowed.
Either way is not ideal.
And often worse, defensive checks are disregarded, leading to vulnerable code
causing real monetary lose.

Apart from investigating effort to audit, certify, or verify smart contract programs,
language designers are responsible to empower programmers with better
linguistic solution to write invulnerable smart contracts in the first place.
In this paper, we argue that advanced \emph{behavioral contracts} provide a
lightweight solution for many security issues found in smart contract programs.

>>>>

Smart contracts are programs to automate the execution of agreement so that all
parties involved in the agreement can be certain about the outcome.
Smart contracts are ``smart'' since by using blockchains they provide a
mechanism to \emph{ensure the economic outcome of transactions} without a
central authority.
A blockchain is a \note{XXX} that implements a consensus protocol of
Byzantine-fault-tolerant distributed ledgers.

@@

Indeed, we have seen a great number of notorious attacks to smart contract
systems in recent years.
For example, Solidity provides first-order assertion primitives @require@ and
@assert@, but they cannot check function values (e.g. used as callbacks), which are a
common pattern used in smart contract programs. Attackers are able to utilize
the callback mechanism to \note{do crazy things and steal money}
Solidity also provides the @modifier@ mechanism that intercepts
before and after a function call, thus can be used to check
pre- and post-conditions.
\todo{can we compose modifier?}
\todo{can we attach modifier to callbacks?}
\todo{can we use modifier to check function's argument?}

The lack of sufficient linguistic means to specify and enforce subtle behaviors
discourages programmers to use concise higher-level abstractions when writing
smart contract code.
Instead, to be secure, programmers are obliged to write verbose code with
lower-level abstractions, which conflates the main business logic and
behavioral checks, leading to poor readability and maintainability.
For instance, to defend the famous DAO attack \note{cite} caused by allowing ``reentrancy''
via external functions, programmers have to be extra cautious about the execution
order or maintain additional states to check if a call is allowed.
Either way is not ideal.
And often worse, defensive checks are disregarded, leading to vulnerable code
causing real monetary lose.

Apart from investigating effort to audit, certify, or verify smart contract programs,
language designers are responsible to empower programmers with better
linguistic solutions to write invulnerable smart contracts in the first place.
In this paper, we show that advanced \emph{behavioral software contracts} provide a
lightweight solution for securing \emph{smart contracts}.
